%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Rahul Chauhan (http://rahulchauhan.net)
%
% Original repository:
% https://github.com/rahulworld/rahulworld-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{rahulworld-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Rahul Chuahan}\\
\end{large}
Final Year (B.Tech)\\
Computer Science $\&$  Engineering\\ 
at NIT Srinagar \\ 
CGPA:8.039 till 7th Sem 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}

Github:// \href{https://github.com/rahulworld}{\custombold{rahulworld}} \\
LinkedIn://  \href{https://www.linkedin.com/in/rahulworld}{\custombold{rahulworld}} \\
Behance://  \href{https://www.behance.net/rahul_world}{\custombold{rahul\_world}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
GNU/Linux, Windows
\vspace{6pt}
\subsection{Languages}
C/C++, Java, Python, javascript
\vspace{6pt}
\subsection{Framework}
Flask, ExtJS, \\Node.js, Android,
Web-development
\vspace{6pt}
\subsection{Databases}
MySQL, PostgreSQL, MangoDB
\vspace{6pt}
\subsection{Others}
Markdown, Git, Vim, \\Sublime Text, Eclipse,\\
Android Studio, Coral Draw,\\
Adobe Illustrator, Photoshop
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures\\
Algorithm\\
Neural Networks\\
Discrete Mathematics\\
Operating Systems\\
MySQL\\
Data Analysis
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{20XX-20YY}
\subsection{B.Tech. in CSE}
NIT SRINAGAR \\
CGPA : 8.05/10(Expected)\\
\vspace{8pt}
\datecolor{20XX-20YY}
\subsection{Intermediate}
Hame Convent Inter College, FZD\\
Percentage: 80.8\%\\
\vspace{8pt}
\datecolor{20XX-20YY}
\subsection{High School}
Hame Convent Inter College, FZD\\
Percentage: 81\%
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill J-90, NIT Srinagar, Hazaratbal \\
\hspace*{0pt}\hfill Srinagar, J$\&$ K-190 006, India \\
\hspace*{0pt}\hfill Mob.: +91-8449368522 \\
\hspace*{0pt}\hfill Email.:\textbf{\href{mailto:rahulnitsxr@gmail.com}{rahulnitsxr@gmail.com}} \\
\hspace*{0pt}\hfill Web.:\textbf{\href{http://rahulchauhan.net}{http://rahulchauhan.net}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{OSGeo}
\descript{Google Summer of Code 2018 Student Developer Intern }
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Support of Unit of Measure conversion in istSOS3: My project is to add conversion of
unit of measure in istsos3. User can convert unit in another specified unit.
\end{minipage}
\descriptright{Python, PostgreSQL, Pandas, Numpy, Scipy, Pint, Postgresql-unit, Javascript}
\sectionsep

\datecolor{20XX-now} \runsubsection{OSGeo}
\descript{Google Summer of Code 2017 Student Developer Intern }
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Data analysis and statastical tool suit: istsos2 provides easily manage your sensor network
and distribute your data in a standard way. which is be used to automate the creation of statisticate
documents using OAT(Observation analysis tool) and harvesting the data from an istSOS server.
\end{minipage}
\descriptright{ExtJS, Dygraph.js, D3.js, Data analysis, Python, PostGIS, Pandas, Numpy, Scipy}
\sectionsep

\datecolor{20XX-now} \runsubsection{Indian Institute of Science, Banglore}
\descript{Research Intern}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
pan sharpening is one kind of data fusion become very wide spread method which populate the spectral band information with the influence of high spatial information.
\end{minipage}
\descriptright{Satellite images(Chandrayan), Fusion Algorithm, Java}
\sectionsep

\datecolor{20XX-now} \runsubsection{Smokey, Banglore}
\descript{Android Intern}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Worked on location based services application which provide services at any location near
services provider and also made friend module.
\end{minipage}
\descriptright{Android, Mysql, Google map}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Awards} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{Rajsthan Hackathon}
\descript{Participated}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this hackathon Developed distributed Voting Application.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Angelhack, Jaipur}
\descript{Finalist}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this hackathon Developed a Dapp using Blockchain which is based on smart contract.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Digital India}
\descript{Grand Prize Winner}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this hackathon developed a web-app in which showing kashmir as paradise on earth.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Project}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{Digital Certificate Dapp using Ethereum}
\descript{Blockchain, Web3JS}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A Dapp issue certificate and verify. An Idea to use Blockchain to create Digital Certificate.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Identifying Gender From Images of Faces}
\descript{ML}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Identifying gender of a person by looking at his/her Photograph.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Small Project}
\descript{Android, Data Analysis, Image Processing}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Result Portal, Voice Calci, Cubic Bispline, Image Compression, smoothing, Fitting Curve.
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}